---
title: "Data Analysis Notes: Facebook Dashboard"
author: "Jonathan L Marrero"
output: html_document
---

```{r echo=FALSE}
require(ggplot2)

source("timeClean.R")
source("getData.R")

require(lubridate)

# if (getwd() != "/Users/Marrero/Downloads") {
#  setwd("Downloads")
# }

pageDataPath <- "data/fb_test_datapage.csv"
postDataPath <- "data/fb_post_data.csv"


## Splitting the date and time into separate parts 
post <- getPostData(postDataPath)
page <- getPageData(pageDataPath)


postTimeParts <- timeClean(post$Posted)
page$Date <- as.Date(page$Date)

post <- post[1:46]

post$Posted <- as.Date(postTimeParts$V1, format = "%m/%d/%Y")
post$Time <- postTimeParts$V2
post$AMPM <- postTimeParts$V3
post$Month <- postTimeParts$V4
post$Weekday <- postTimeParts$V5
```

Total number of people who engaged with our posts: 
```{r echo=FALSE} 
n1 <- sum(post$Lifetime.Post.Total.Reach)
n1
```


Number of engagements by post type:
```{r echo=FALSE}
tapply(post$Lifetime.Engaged.Users, post$Type, FUN = sum)
barplot(tapply(post$Lifetime.Engaged.Users, post$Type, sum))
```

The number of our followers reached by our post:  
```{r echo=FALSE} 
n2 <- sum(post$Lifetime.Post.reach.by.people.who.like.your.Page)
n2
```

How many times do we post in the morning compared to the evening?
```{r echo=FALSE}
barplot(table(post$AMPM))
```

How many people did we reach by post type?
```{r echo=FALSE}
tapply(post$Lifetime.Post.Total.Reach, post$Type, FUN=sum)
```

How many people did we reach in the morning, afternoon, and evening? 
```{r echo=FALSE}
tapply(post$Lifetime.Post.Total.Reach, post$AMPM, FUN=sum)
barplot(tapply(post$Lifetime.Post.Total.Reach, post$AMPM, FUN=sum)/1000, ylab = "Post Reach x 1,000", main = "Reach by Time of Day", col = "skyblue")
```

Total posts by AM or PM:
```{r echo=FALSE}
barplot(table(post$AMPM))
```

Total posts by weekday:
```{r echo=FALSE}
table(post$Weekday)
barplot(table(post$Weekday))
```

Reach by weekday: 
```{r echo=FALSE}
tapply(post$Lifetime.Post.Total.Reach, post$Weekday, FUN=sum)
barplot(tapply(post$Lifetime.Post.Total.Reach, post$Weekday, FUN=sum)/1000)
```

Average reach in the AM and PM:
```{r echo=FALSE}
barplot(tapply(post$Lifetime.Post.Total.Reach, post$AMPM, mean)/1000)
```

Total number of links clicked: (i.e., traffic generated)
```{r echo=TRUE}
sum(post$Lifetime.Post.consumers.by.type...link.clicks, na.rm = TRUE)
```

Total posts by month:
```{r echo=FALSE}
table(post$Month)
barplot(table(post$Month))
```

Total number of new likes by month: 
```{r echo=FALSE}
tapply(page$Daily.New.Likes, month(page$Date, label = TRUE), sum)
barplot(tapply(page$Daily.New.Likes, month(page$Date, label = TRUE), sum))
```